Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-24 ijar-npb-ms.tex
Corrections and improvements to theory.

@@

Based on expert assumptions for component failure distributions and component test data,
we make predictive inference for a system with components that are exchangeable
with the test components by calculating the system reliability function $\Rsys(t) = P(\Tsys > t)$.
Considering a discrete grid of time points $\{t_1, \ldots, \tmax\}$,
naturally a Bayesian model for the functioning probability at each time point arises (see Section~\ref{sec:nonparamapproach}).
To account for uncertainty in the choice of prior
and due to the inherent issue with prior-data conflict (see below / Section~\ref{sec:reparam}),
we propose an imprecise probability approach
based on sets of prior distributions defined through sets of canonical parameters.
This approach also allows to adequately model weak or partial prior information.
In particular, prior near ignorance can be modelled much more naturally than through usual so-called noninformative priors.

%Our imprecise probability approach leads to sets of system reliability functions,
%where the magnitude of the set, i.e., the width of the posterior predictive functioning probability interval
%reflects the precision of the reliability estimate:
%a short range will indicate that we can quantify the reliability of the system quite precisely,
%while a large range will indicate that our (probabilistic) knowledge is rather shaky --
%remember that the reliability function is in essence a collection of probability statements.
Our imprecise probability approach leads, for each $t$ in some grid of time points ${\cal T}$,
to a posterior predictive probability interval for the event that the system will function at time $t$.
The width of these intervals reflects the precision of the probability statement:
a short range will indicate that we can quantify the system functioning probability quite precisely,
while a large range will indicate that our (probabilistic) knowledge is indeterminate.

@@

As we will show in Section~\ref{sec:reparam}, when taking the standard choice of a conjugate Beta prior,
prior-data conflict is ignored, as the spread of the posterior distribution does not increase in case of such a conflict,
ultimately conveying a false sense of certainty
by communicating that we can quantify the reliability of the system quite precisely when in fact we cannot do so.
In contrast, our method will indicate prior-data conflict by wider bounds for $\Rsys(t)$.
This behaviour is obtained by a specific choice for the set of priors (see Section~\ref{sec:setsofbetapriors})
which leads to larger sets of posterior distributions when prior knowledge and data are in conflict.

@@

There are several relatively straightforward generalizations of the use of the survival signature.
The probabilities for the numbers of functioning components can be generalized to lower and upper probabilities,
as e.g.\ done by \citet{CCMA14} within the nonparametric predictive inference (NPI) framework of statistics \citep{Co11},
where lower and upper probabilities for the events $C_k = l_k$
are inferred from test data on components of the same types as those in the system.
This is an approach that is also followed in the current paper, but with the use of generalized Bayesian inference instead of NPI.
Like \citet{CCMA14}, we will utilize the monotonicity of the survival signature for coherent systems
to simplify computations.

@@

The analogous result for $\nktz$ is more subtle, because stochastic 
dominance is not guaranteed at a single value.  The following Theorem 
provides the conditions under which an upper or lower limit has first-order stochastic dominance.

\begin{theorem}
  \label{thm:n}
  Let $\beta_n$ denote the Beta-Binomial distribution with probability mass function parameterised as:
  \[ p(l \mid y, n, m, s, N) \propto \frac{B(l + ny + s, m - l + n(1-y) + N - s)}{B(ny + s, n(1-y) + N - s)}, \]
  with $y, m, s,$ and $N$ fixed and unknown.  
  Then,
  \[ y > \frac{s + m}{N + m - 1} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
  and 
  \[ y < \frac{s}{N + m - 1} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
  If $\frac{s}{N + m - 1} < y < \frac{s + m}{N + m - 1}$ then first-order stochastic dominance is not guaranteed.
\end{theorem}
The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:n}.

These first-order stochastic domination results now gives the exact 
solution for $\lRsys(\cdot)$ and $\uRsys(\cdot)$.  Thus,
%For $\lRsys(\cdot)$, the minimum is achieved at
%$\nktzu$ if $\yktzl(n_k+m_k-1)-s^k_t-m_k < 0$ and is achieved at 
%$\nktzl$ if $\yktzl(n_k+m_k-1)-s^k_t-m_k > 0$.
%Conversely, for $\uRsys(\cdot)$, the maximum is achieved at 
%$\nktzu$ if $\yktzu(n_k+m_k-1)-s^k_t-m_k > 0$ and is achieved at 
%$\nktzl$ if $\yktzu(n_k+m_k-1)-s^k_t-m_k < 0$.
\begin{align}
\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)} \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktz\yktz + s^k_t, m_k - l_k + \nktz(1-\yktz) + n_k - s^k_t)}{B(\nktz\yktz + s^k_t, \nktz(1-\yktz) + n_k - s^k_t)}
    \nonumber\\
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktzo\yktzl + s^k_t, m_k - l_k + \nktzo(1-\yktzl) + n_k - s^k_t)}{B(\nktzo\yktzl + s^k_t, \nktzo(1-\yktzl) + n_k - s^k_t)} \label{eq:LwrSysPost}\\
 &\qquad \qquad \mbox{where } \nktzo = \left\{ \begin{aligned}
   \nktzu & \quad\mbox{if}\quad \yktzl < \frac{s}{N + m - 1} \\
   \nktzl & \quad\mbox{if}\quad \yktzl > \frac{s + m}{N + m - 1} \\
   \mathrm{optimised} & \quad\mbox{if}\quad \frac{s}{N + m - 1} < \yktzl < \frac{s + m}{N + m - 1}
 \end{aligned} \right. \nonumber
\end{align}

@@

As example to illustrate the potential of our model,
we consider a simplified automotive brake system.
The master brake cylinder (M) activates all four wheel brake cylinders (C1 -- C4),
which in turn actuate a braking pad assembly each (P1 -- P4).
The hand brake mechanism (H) goes directly to the brake pad assemblies P3 and P4;
the car brakes when at least one brake pad assembly is actuated.
The system layout is depicted in Figure~\ref{fig:brakesystem},
together with prior and posterior sets of reliability functions for the four component types and the complete system.
Observed lifetimes from test data are indicated by tick marks in each of the four component type panels,
where $n_\text{M}=5$, $n_\text{H}=10$, $n_\text{C}=15$, and $n_\text{P}=20$.
We assume $[\ntzl{\text{M}},\ntzu{\text{M}}] = [1,8]\ \forall t$,
and $[\nktzl, \nktzu] = [1,2]$ for $k \in \{\text{H, C, P}\}$ and all $t$.
Prior functioning probability bounds for M are based on
a Weibull cdf with shape $2.5$ and scales $6$ and $8$ for the lower and upper bound, respectively.
The prior bounds for P can be seen as the least committal bounds
derived from an expert statement of $\ytz{\text{P}} \in [0.5, 0.65]$ for $t=5$ only.

***We see that posterior lower and upper functioning probabilities drop at those times $t$
for which there is a failure time in the test data,
or a drop in the prior functioning probability bounds.
The lower bound for prior system reliability drops to zero at $t=5$
since the prior lower bound for P drops to zero at $t=5$;
for the system to function, at least one brake pad assembly must function.***

For H, near-noninformative prior functioning probability bounds have been selected;
with the upper bound for P being approximately one for $t \le 5$ as well,
the prior upper system reliability bound for $t \le 5$ is close to one, too,
since the system can function on H and one of P1 -- P4 alone.
Note that the posterior functioning probability interval for M
is wide not only due to the limited number of observations,
but also because $\ntzu{\text{M}} = 8$ and the prior-data conflict reaction.

Posterior functioning probability bounds for the complete system
are much more precise than the prior system bounds,
reflecting the information gained from component test data.
The posterior system bounds can be also seen to reflect location and precision of the component bounds;
for example, the system bounds drop drastically between $t=2.5$ and $t=3.5$
mainly due to the drop of the bounds for P at that time.

\begin{figure}
\begin{tikzpicture}
[typeM/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
 typeC/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
 typeP/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
 typeH/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
 cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
 hv path/.style={thick, to path={-| (\tikztotarget)}},
 vh path/.style={thick, to path={|- (\tikztotarget)}}]
\node at (0,0) {\includegraphics[width=\textwidth]{brakingsystem-2}};
\begin{scope}[scale=1.00,xshift=3.4cm,yshift=-1.1cm]
\node[typeM] (M)    at ( 0  , 0  ) {M};
\node[typeC] (C1)   at ( 1  , 1.5) {C1};
\node[typeC] (C2)   at ( 1  , 0.5) {C2};
\node[typeC] (C3)   at ( 1  ,-0.5) {C3};
\node[typeC] (C4)   at ( 1  ,-1.5) {C4};
\node[typeP] (P1)   at ( 2  , 1.5) {P1};
\node[typeP] (P2)   at ( 2  , 0.5) {P2};
\node[typeP] (P3)   at ( 2  ,-0.5) {P3};
\node[typeP] (P4)   at ( 2  ,-1.5) {P4};
\node[typeH] (H)    at ( 0  ,-1  ) {H};
\coordinate (start)  at (-0.7, 0);
\coordinate (startC) at ( 0.5, 0);
\coordinate (startH) at (-0.4, 0);
\coordinate (Hhop1)  at ( 0.4,-1);
\coordinate (Hhop2)  at ( 0.6,-1);
\coordinate (endP)   at ( 2.5, 0);
\coordinate (end)    at ( 2.8, 0);
\path (start)     edge[hv path] (M.west)
      (M.east)    edge[hv path] (startC)
      (startC)    edge[vh path] (C1.west)
                  edge[vh path] (C2.west)
                  edge[vh path] (C3.west)
                  edge[vh path] (C4.west)
      (C1.east)   edge[hv path] (P1.west)
      (C2.east)   edge[hv path] (P2.west)
      (C3.east)   edge[hv path] (P3.west)
      (C4.east)   edge[hv path] (P4.west)
      (endP)      edge[vh path] (P1.east)
                  edge[vh path] (P2.east)
                  edge[vh path] (P3.east)
                  edge[vh path] (P4.east)
                  edge[hv path] (end)
      (startH)    edge[vh path] (H.west)
      (H.east)    edge[hv path] (Hhop1)
      (Hhop1)     edge[thick,out=90,in=90] (Hhop2)
      (Hhop2)     edge[hv path] (P3.south)
                  edge[hv path] (P4.north);
\end{scope}
\end{tikzpicture}
\caption{Prior and posterior sets of reliability functions for a simplified automotive brake system
with layout as depicted in the lower right panel.}
\label{fig:brakesystem}
\end{figure}

@@

The survival signature and its use for uncertainty quantification for system
reliability can be generalized quite straightforwardly, mainly due to the simplicity of this concept.
For example, one may generalize the system structure function from a binary function to a probability, %\citep[see]{CCM16},
to reflect uncertainty about system functioning for known states of its components, with a further
generalization to imprecise probabilities possible. It is also conceptually easy to generalize the
survival signature to multi-state systems such that it again summarizes the structure function
in a manner that is sufficient for a range of uncertainty quantifications for the system reliability.

***Extend the model to deal with right-censored observations which are common in the reliability setting.
The minimal assumption that a component can either fail immediately after censoring or live forever
will be simple to implement but will lead to high imprecision,
whereas assuming exchangeability with other surviving components at moment of censoring
will be more complex to accomodate but will lead to less imprecision.
This excangeability assumption lies at the core of the Kaplan-Meier estimator \citep{1958:kaplan-meier},
and has already been adopted by \citet{2004:coolen-yan} in an imprecise probability context.

@@

@@

  However, unlike the case for the $y$ parameter in Theorem \ref{thm:y}, neither $\beta_{\nl}$ 
  nor $\beta_{\nu}$ can be guaranteed to dominate for all possible values 
  for the other parameters, so that necessary conditions for
  monotonicity (either increasing or decreasing) must be established.
  We require,
  \[ \frac{(l + \nu y + s) (m - l - 1 + \nl (1 - y) + N - s)}
          {(l + \nl y + s) (m - l - 1 + \nu (1 - y) + N - s)}
     >1
  \]
  After extensive routine algebra, this can be conveniently expressed as
  \begin{align*}
    (\nu - \nl)[y (N + m - 1) - s] - l (\nu - \nl)>0.
  \end{align*}
  This limit is hardest to satisfy for $l=m$ since $\nu-\nl>0$.
  Thus, for monotonicity to hold for all $l$, we require
  \begin{align*}
    (\nu - \nl)[y (N + m - 1) - s] - m (\nu - \nl) &>0 \\
    \implies (\nu - \nl)[y (N + m - 1) - s - m] &>0
  \end{align*}
  Since $\nu-\nl>0$ by definition, we have a monotonically increasing 
  likelihood ratio only when \[ y (N + m - 1) - s - m > 0. \]
  By a similar argument, the likelihood ratio is only monotonically decreasing when
  \[ y (N + m - 1) - s < 0. \]
  Thus,
  \[ y > \frac{s + m}{N + m - 1} \implies \beta_{\nu} \ge_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
  and 
  \[ y < \frac{s}{N + m - 1} \implies \beta_{\nu} \le_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
  by \cite[Theorem 1.C.1, p.43]{shaked2007}.  In the intermediate case,
  \[ \frac{s}{N+m-1} < y < \frac{s+m}{N+m-1} \]
  we cannot definitively state the stochastic ordering on $\beta_{\nu}$ and $\beta_{\nl}$.
\end{proof}

>>>>

\usepackage{mathtools}

@@

Based on expert assumptions for component failure distribution and component test data,
we make predictive inference for a system with components that are exchangeable
with the test components by calculating the system reliability function $\Rsys(t) = P(\Tsys > t)$.
Considering a discrete grid of time points $\{t_1, \ldots, \tmax\}$,
naturally a Bayesian model for the functioning probability at each time point arises (see Section~\ref{sec:nonparamapproach}).
To account for uncertainty in the choice of prior
and due to the inherent issue with prior-data conflict (see below / Section~\ref{sec:reparam}),
we propose an imprecise or interval probability approach
based on sets of prior distributions defined through sets of canonical parameters.
This approach also allows to adequately model weak or partial prior information.
In particular, prior near ignorance can be modelled much more naturally than through usual so-called noninformative priors.

Our imprecise probability approach leads to sets of system reliability functions,
where the magnitude of the set, i.e., the width of the posterior predictive functioning probability interval
reflects the precision of the reliability estimate:
a short range will indicate that we can quantify the reliability of the system quite precisely,
while a large range will indicate that our (probabilistic) knowledge is rather shaky --
remember that the reliability function is in essence a collection of probability statements.

@@

As we will show in Section~\ref{sec:reparam}, when taking the standard choice of a conjugate Beta prior,
prior-data conflict is ignored, as the spread of the posterior distribution does not increase in case of such a conflict,
ultimately conveying a false sense of certainty
by communicating that we can quantify the reliability of the system quite precisely when in fact we can not.
In contrast, our method will indicate prior-data conflict by wider bounds for $\Rsys(t)$.
This behaviour is obtained by a specific choice for the set of priors (see Section~\ref{sec:setsofbetapriors})
which leads to larger sets of posterior distributions when prior knowledge and data are in conflict.

@@

There are several relatively straightforward generalizations of the use of the survival signature.
The probabilities for the numbers of functioning components can be generalized to lower and upper probabilities,
as e.g.\ done by \citet{CCMA14} within the nonparametric predictive inference (NPI) framework of statistics \citep{Co11},
where lower and upper probabilities for the events $C_k = l_k$
are inferred from test data on components of the same types as those in the system.
This is an approach that is also followed in the current paper, but with the use of generalized Bayesian inference instead of NPI.
***This step is less trivial here as we must ensure to have probability distributions for these events,
thus summing to one over $l_k=0,1,\ldots,m_k$ for each type $k$.
***covered because of parametric distribution, min and max over parameter sets (see section 6)***
***For coherent systems this is not very complicated due to the monotonicity of the survival signature,
see \citet{CCMA14} where the method for dealing with imprecision on the random quantities $C_k$ is presented.***
\td{Leave out the sentences framed with `***'?}
Recently, \citet{CCM16} suggested the generalization of the structure function from a binary function to a probability,
to reflect uncertainty about system functioning for known states of its components.
A further suggestion was to generalize this to lower and upper structure functions,
within the theory of imprecise probability \citep{itip,CU11}.
These suggestions are also easy to incorporate into system reliability with the use of the survival signature,
which in the latter case also becomes an imprecise probability.

The survival signature is a powerful but rather basic concept.
As such, further generalizations are conceptually easy,
for example one can straightforwardly generalize the survival signature to multi-state systems
such that it again summarizes the structure function
in a manner that is sufficient for a range of uncertainty quantifications for the system reliability.

@@

The analogous result for $\nktz$ is more subtle, because stochastic 
dominance is not guaranteed at a single value.  The following Theorem 
provides simple sufficient conditions under which an upper or lower 
limit has first-order stochastic dominance and has virtually no 
computational overhead to test.

\begin{theorem}
  \label{thm:n}
  Let $\beta_n$ denote the Beta-Binomial distribution with probability mass function parameterised as:
  \[ p(l \mid y, n, m, s, N) \propto \frac{B(l + ny + s, m - l + n(1-y) + N - s)}{B(ny + s, n(1-y) + N - s)}, \]
  with $y, m, s,$ and $N$ fixed and unknown.  
  Then,
  \[ y > \frac{s + m - 1}{N + m - 1} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
  and 
  \[ y < \frac{s}{N + m - 1} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
\end{theorem}
The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:n}.

If $\frac{s}{N + m - 1} < y < \frac{s + m - 1}{N + m - 1}$ then 
Theorem 2 cannot determine stochastic dominance.  The following slightly
more computationally costly Lemma may be able to determine first-order
stochastic dominance in such situations.
\begin{lemma}
  \label{lem:n}
  Let $\beta_n$ denote the Beta-Binomial distribution as in Theorem \ref{thm:n}.  Define
  \[ \mathcal{L}_{\nu,\nl}(l) := \frac{p(l \mid y, \nu, m, s, N)}{p(l \mid y, \nl, m, s, N)} \]
  Then,
  \[ \left. \begin{aligned}
       \mathcal{L}_{\nu,\nl}(0) \le 1 \\
       \mathcal{L}_{\nu,\nl}(m) \ge 1 \\
    \end{aligned} \right\}
    \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
  and
  \[ \left. \begin{aligned}
       \mathcal{L}_{\nu,\nl}(0) \ge 1 \\
       \mathcal{L}_{\nu,\nl}(m) \le 1 \\
    \end{aligned} \right\}
    \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
\end{lemma}
The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:n2}.
In the cases where neither Theorem \ref{thm:n} or Lemma \ref{lem:n} apply,
the entire posterior system reliability function must be optimised to 
find the minima/maxima.
In practise, in the examples to be presented in the sequel, Theorem 
\ref{thm:n} and Lemma \ref{lem:n} do provide guarantees of first-order
stochastic dominance for the vast majority of time points, $t$,
substantially lowering the computational costs of performing the
minimisation/maximisation involved in finding the sets of system 
reliability functions compared to either numerical optimisation or
an exhaustive grid search (which would get exponentially slower in 
the number of different components).

Thus,
%For $\lRsys(\cdot)$, the minimum is achieved at
%$\nktzu$ if $\yktzl(n_k+m_k-1)-s^k_t-m_k < 0$ and is achieved at 
%$\nktzl$ if $\yktzl(n_k+m_k-1)-s^k_t-m_k > 0$.
%Conversely, for $\uRsys(\cdot)$, the maximum is achieved at 
%$\nktzu$ if $\yktzu(n_k+m_k-1)-s^k_t-m_k > 0$ and is achieved at 
%$\nktzl$ if $\yktzu(n_k+m_k-1)-s^k_t-m_k < 0$.
\begin{align}
\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)} \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktz\yktz + s^k_t, m_k - l_k + \nktz(1-\yktz) + n_k - s^k_t)}{B(\nktz\yktz + s^k_t, \nktz(1-\yktz) + n_k - s^k_t)}
    \nonumber\\
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktzo\yktzl + s^k_t, m_k - l_k + \nktzo(1-\yktzl) + n_k - s^k_t)}{B(\nktzo\yktzl + s^k_t, \nktzo(1-\yktzl) + n_k - s^k_t)} \label{eq:LwrSysPost}\\
 &\mathrm{where} \nonumber \\
 &\nktzo = \left\{ \begin{aligned}
   \nktzu & \quad\mbox{if}\ \yktzl < \frac{s^k_t}{n_k + m_k - 1} \vee \Big( \mathcal{L}_{\nktzu,\nktzl}(0) \ge 1 \wedge \mathcal{L}_{\nktzu,\nktzl}(m) \le 1 \Big) \\
   \nktzl & \quad\mbox{if}\ \yktzl > \frac{s^k_t + m_k - 1}{n_k + m_k - 1} \vee \Big( \mathcal{L}_{\nktzu,\nktzl}(0) \le 1 \wedge \mathcal{L}_{\nktzu,\nktzl}(m) \ge 1 \Big) \\
   & \quad\mbox{optimised otherwise}
 \end{aligned} \right. \nonumber
\end{align}

@@

***Another example: simplified automotive breaking system, Figure~\ref{fig:breakingsystem}.
Prior sets and data exemplary only, prior bounds more smooth curves?
The master breaking cylinder (M) activates all four wheel braking cylinders (C1 -- C4),
which in turn actuate a braking pad assembly each (P1 -- P4).
The hand break mechanism (H) goes directly to two brake pad assemblies P3 and P4;
the car breaks when at least one brake pad assembly is actuated.***

\begin{figure}
\begin{tikzpicture}
[typeM/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
 typeC/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
 typeP/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
 typeH/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
 cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
 hv path/.style={thick, to path={-| (\tikztotarget)}},
 vh path/.style={thick, to path={|- (\tikztotarget)}}]
\node at (0,0) {\includegraphics[width=\textwidth]{breakingsystem-2}};
\begin{scope}[scale=1.00,xshift=3.4cm,yshift=-1.1cm]
\node[typeM] (M)    at ( 0  , 0  ) {M};
\node[typeC] (C1)   at ( 1  , 1.5) {C1};
\node[typeC] (C2)   at ( 1  , 0.5) {C2};
\node[typeC] (C3)   at ( 1  ,-0.5) {C3};
\node[typeC] (C4)   at ( 1  ,-1.5) {C4};
\node[typeP] (P1)   at ( 2  , 1.5) {P1};
\node[typeP] (P2)   at ( 2  , 0.5) {P2};
\node[typeP] (P3)   at ( 2  ,-0.5) {P3};
\node[typeP] (P4)   at ( 2  ,-1.5) {P4};
\node[typeH] (H)    at ( 0  ,-1  ) {H};
\coordinate (start)  at (-0.7, 0);
\coordinate (startC) at ( 0.5, 0);
\coordinate (startH) at (-0.4, 0);
\coordinate (Hhop1)  at ( 0.4,-1);
\coordinate (Hhop2)  at ( 0.6,-1);
\coordinate (endP)   at ( 2.5, 0);
\coordinate (end)    at ( 2.8, 0);
\path (start)     edge[hv path] (M.west)
      (M.east)    edge[hv path] (startC)
      (startC)    edge[vh path] (C1.west)
                  edge[vh path] (C2.west)
                  edge[vh path] (C3.west)
                  edge[vh path] (C4.west)
      (C1.east)   edge[hv path] (P1.west)
      (C2.east)   edge[hv path] (P2.west)
      (C3.east)   edge[hv path] (P3.west)
      (C4.east)   edge[hv path] (P4.west)
      (endP)      edge[vh path] (P1.east)
                  edge[vh path] (P2.east)
                  edge[vh path] (P3.east)
                  edge[vh path] (P4.east)
                  edge[hv path] (end)
      (startH)    edge[vh path] (H.west)
      (H.east)    edge[hv path] (Hhop1)
      (Hhop1)     edge[thick,out=90,in=90] (Hhop2)
      (Hhop2)     edge[hv path] (P3.south)
                  edge[hv path] (P4.north);
\end{scope}
\end{tikzpicture}
\caption{Prior and posterior sets of reliability functions for a simplified automotive breaking system
with layout as depicted in the lower right panel.}
\label{fig:breakingsystem}
\end{figure}

@@

***Extend the model to deal with right-censored observations which are common in the reliability setting.
We believe that a minimal assumption (component can fail immediately after censoring or live forever)
will be simple to implememt but will lead to high imprecision,
whereas assuming exchangeability with other surviving components at moment of censoring
will be more complex to accomodate but will lead to less imprecision.

@@

%\begin{lemma}
%  \label{lm:ineq}
%  Let $a, b > 0$.  Then, \[ b > a \quad \iff \quad \frac{a}{b} < \frac{a \xi + \varepsilon}{b \xi + \varepsilon} \quad \forall \  \xi, \varepsilon > 0 \]
%\end{lemma}
%\begin{proof}
%  Since everything is strictly positive, the proof follows trivially:
%  \begin{align*}
%    \frac{a}{b} &< \frac{a \xi + \varepsilon}{b \xi + \varepsilon} \\
%    \iff \quad a b \xi + a \varepsilon &< a b \xi + b \varepsilon \\
%    \iff \quad a &< b
%  \end{align*}
%\end{proof}

@@

  However, unlike the case for the $y$ parameter in Theorem \ref{thm:y}, neither $\beta_{\nl}$ 
  nor $\beta_{\nu}$ can be guaranteed to dominate for all possible values 
  for the other parameters, so that necessary conditions for
  monotonicity (either increasing or decreasing) must be established.
  We require,
  \[ \frac{(l + \nu y + s) (m - l - 1 + \nl (1 - y) + N - s)}
          {(l + \nl y + s) (m - l - 1 + \nu (1 - y) + N - s)}
     >1
  \]
  After extensive routine algebra, this can be conveniently expressed as
  \begin{align*}
    (\nu - \nl)[y (N + m - 1) - s] - l (\nu - \nl)>0.
  \end{align*}
  This limit is hardest to satisfy for $l=m-1$ since $\nu-\nl>0$ (note $l\ne m$ since we are evaluating $\mathcal{L}(l+1)/\mathcal{L}(l)$, so $m-1$ is the maximal value $l$ can take).
  Thus, for monotonicity to hold for all $l$, we require
  \begin{align*}
    (\nu - \nl)[y (N + m - 1) - s] - (m - 1) (\nu - \nl) &>0 \\
    \implies (\nu - \nl)[y (N + m - 1) - s - m + 1] &>0
  \end{align*}
  Since $\nu-\nl>0$ by definition, we have a monotonically increasing 
  likelihood ratio only when \[ y (N + m - 1) - s - m + 1 > 0. \]
  By a similar argument, the likelihood ratio is only monotonically decreasing when
  \[ y (N + m - 1) - s < 0. \]
  Thus,
  \begin{equation}
    y > \frac{s + m - 1}{N + m - 1} \implies \beta_{\nu} \ge_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl}
    \label{eq:nuDOMnl}
  \end{equation}
  and 
  \begin{equation}
    y < \frac{s}{N + m - 1} \implies \beta_{\nu} \le_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} 
    \label{eq:nlDOMnu}
  \end{equation}
  by \cite[Theorem 1.C.1, p.43]{shaked2007}.  In the intermediate case,
  \[ \frac{s}{N+m-1} < y < \frac{s+m-1}{N+m-1} \]
  standard likelihood ratio ordering theory cannot definitively state
  the stochastic ordering on $\beta_{\nu}$ and $\beta_{\nl}$.
\end{proof}

\begin{proof}[\textbf{Proof of Lemma \ref{lem:n}, p\pageref{lem:n}}]
  \label{prf:n2}
  \eqref{eq:nuDOMnl} and \eqref{eq:nlDOMnu}
  are sufficient but not necessary conditions.  Using theory in 
  \cite{klenke2010} we can sharpen these conditions to provide
  first-order stochastic dominance conditions for a larger range of
  parameter values.

  Proposition 2.1, p.399 of \cite{klenke2010} proves that half-monotone
  likelihood ratio ordering --- i.e.\ monotonicity of $\mathcal{L}(l+1) / \mathcal{L}(l)$ ---
  together with left and right tail conditions on $\mathcal{L}(\cdot)$
  imply first order stochastic dominance.

  \medskip
  \noindent{\emph{Half-monotonicity of $\mathcal{L}(\cdot)$}}

  Although there exist parameters for which $\mathcal{L}(\cdot)$ is
  not monotone, it is half-monotone.  That is, $\mathcal{L}(l+1) / \mathcal{L}(l)$ is itself monotone.  For simplicity, write
  \begin{align*}
    \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} = \frac{(l + \pu)(\el - l)}{(l + \pl)(\eu - l)}
    \quad \mbox{where} \left\{\begin{aligned}
      \pu &= \nu y + s \\
      \pl &= \nl y + s \\
      \eu &= m - 1 + \nu (1 - y) + N - s \\
      \el &= m - 1 + \nl (1 - y) + N - s
    \end{aligned} \right.
  \end{align*}
  Then,
  \begin{align*}
    \frac{\mathcal{L}(l+2)/\mathcal{L}(l+1)}{\mathcal{L}(l+1)/\mathcal{L}(l)} =
    \frac{(\pl + l)(\pu + l + 1)(\el - l - 1)(\eu - l)}
           {(\pl + l + 1)(\pu + l)(\el -
l)(\eu - l - 1)}
    &> 1 \\
    \iff \qquad \frac{\pl + l}{\pu + l} \cdot \frac{\el - l - 1}{\eu - l - 1} 
    &> \frac{\pl + l + 1}{\pu + l + 1} \cdot \frac{\el -
l}{\eu - l}
  \end{align*}
  But, $\pu > \pl > 0$, $\eu > \el > 0$, $l > 0$, %and Lemma \ref{lm:ineq} (p.\pageref{lm:ineq}) with $\xi=\varepsilon=1$ imply
  so it is trivial to prove
  \[
    \frac{\pl + l}{\pu + l} > \frac{\pl + l + 1}{\pu + l + 1} \qquad\mbox{and}\qquad \frac{\el - l - 1}{\eu - l - 1} > \frac{\el -
l}{\eu - l} \qquad \forall\ l \in \{0,\dots,m\}
  \]
  Thus we can conclude that $\mathcal{L}(\cdot)$ is half monotone increasing.

  \medskip
  \noindent{\emph{Tail conditions on $\mathcal{L}(\cdot)$}}

  It is not difficult to derive the same loose bounds as in Theorem \ref{thm:n}
  using the tail conditions.  However, it is also easy to see that 
  these are sufficient but not necessary.  Sharpening these bounds
  in terms of the other parameter values involves seemingly intractable
  algebra, so we leave the tail condition as the alternative slightly 
  more costly numerical check when the conditions of Theorem
  \ref{thm:n} are not satisfied.  Evaluation of $\mathcal{L}(\cdot)$ 
  at two values is still orders of magnitude less costly than 
  reevaluation of $\lRsys(\cdot)$ or $\uRsys(\cdot)$.
\end{proof}
%  \medskip
%  \noindent{\emph{ii) Left tail condition $\mathcal{L}(0) \le 1$}}
%
%  The second condition is that
%  \begin{align*}
%    \mathcal{L}(0) 
%    &= \frac{\Gamma(m + \nu (1 - y) + N - s) \Gamma(\nl (1 - y) + N - s)}
%            {\Gamma(m + \nl (1 - y) + N - s) \Gamma(\nu (1 - y) + N - s)} \\
%    &\qquad \times \frac{\Gamma(\nu+N) \Gamma(m+\nl+N)}
%                       {\Gamma(\nl+N) \Gamma(m+\nu+N)} \le 1
%  \end{align*}
%  
%  Let, $m=1$, it's minimal possible value.  Then,
%  \begin{align*}
%    &\frac{\Gamma(1 + \nu (1 - y) + N - s) \Gamma(\nl (1 - y) + N - s) \Gamma(\nu + N) \Gamma(1 + \nl + N)}
%            {\Gamma(1 + \nl (1 - y) + N - s) \Gamma(\nu (1 - y) + N - s) \Gamma(\nl + N) \Gamma(1 + \nu + N)} \\
%    &= \frac{(\nu (1 - y) + N - s) (\nl + N)}{(\nl (1 - y) + N - s) (\nu + N)}
%  \end{align*}
%  But,
%  \[ \frac{(\nu (1 - y) + N - s) (\nl + N)}{(\nl (1 - y) + N - s) (\nu + N)} \le 1 \quad\iff\quad y \le \frac{s}{N} \]
%  
%  Assume $y \le s / N$ and $\mathcal{L}(0 \mid m = k) \le 1$.  Then, for $m=k+1$
%  \begin{align*}
%    &\frac{\Gamma(k+1 + \nu (1 - y) + N - s) \Gamma(\nl (1 - y) + N - s) \Gamma(\nu + N) \Gamma(k+1 + \nl + N)}
